01-training and testing data

### 2019-08-14 journals/01-training_and_testing_data/01-training_and_testing_data.Rmd
updated journals after data folder movement

```{r}
# Load in the Hamby 173 and 252 dataset
hamby173and252_raw <- read.csv("../../data/raw/features-hamby173and252.csv") %>%
  filter(study1 != "Cary", study2 != "Cary") %>%
  mutate(study1 = factor(study1), 
         study2 = factor(study2))
```

@@

```{r}
# Save the datasets and response variables as .csv files
write.csv(hamby173and252_train, "../../data/hamby173and252_train.csv", row.names = FALSE)
```

@@

```{r}
# Load in the Hamby 224 datasets
hamby224_set1 <- readRDS("../../data/raw/h224-set1-features.rds")
hamby224_set11 <- readRDS("../../data/raw/h224-set11-features.rds")
```

@@

```{r}
# Save the test data as a .csv file
write.csv(hamby224_test, "../../data/hamby224_test.csv", row.names = FALSE)
```

>>>>

```{r}
# Load in the Hamby 173 and 252 dataset
hamby173and252_raw <- read.csv("../../../data/raw/features-hamby173and252.csv") %>%
  filter(study1 != "Cary", study2 != "Cary") %>%
  mutate(study1 = factor(study1), 
         study2 = factor(study2))
```

@@

```{r eval = FALSE}
# Save the datasets and response variables as .csv files
write.csv(hamby173and252_train, "../../data/hamby173and252_train.csv", row.names = FALSE)
```

@@

```{r}
# Load in the Hamby 224 datasets
hamby224_set1 <- readRDS("../../../data/raw/h224-set1-features.rds")
hamby224_set11 <- readRDS("../../../data/raw/h224-set11-features.rds")
```

@@

```{r eval = FALSE}
# Save the test data as a .csv file
write.csv(hamby224_test, "../../data/hamby224_test.csv", row.names = FALSE)
```
